Fusing Filters with Integer Linear Programming

### 2014-05-07 2014betterfusionforfilters/Main.tex
constraint generation fixes
Another go at size inference constraint generation
Re-written the abstract to make the contribution a bit more explicit

\documentclass[preprint]{sigplanconf}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{mathptmx}
\usepackage{hyperref}
\usepackage{alltt}
\usepackage{url}
\usepackage{float}
\usepackage{style/utils}
\usepackage{style/code}
\usepackage{style/proof}

@@

\begin{abstract}
Recent work on array fusion shows how to extract data-flow graphs from functional programs and compile them into efficient imperative loops. However, the compilation process only handles graphs that can be compiled into \emph{single} loops, and most programs require more. Prior work shows how use Integer Linear Programming (ILP) to \emph{cluster} the operators in a general data-flow graph into subgraphs that can be individually fused, but until now this approach did not handle operations like filter, which produce arrays of a different size than their input. We extend the existing ILP approach with support for size changing operators, using an external ILP solver to find good clusterings.
\end{abstract}

>>>>

\documentclass[preprint]{sigplanconf}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{mathptmx}
\usepackage{stmaryrd}
\usepackage{hyperref}
\usepackage{alltt}
\usepackage{url}
\usepackage{float}
\usepackage{style/utils}
\usepackage{style/code}
\usepackage{style/proof}
\usepackage{style/judgements}

@@

\begin{abstract}
In this paper, we present an array fusion technique for functional programs, which is able to handle multi-loop programs containing size altering operations like filter. Recent work on array fusion shows how to extract data-flow graphs from functional programs and compile them into efficient imperative loops.  However, the compilation process only handles graphs that can be compiled into \emph{single} loops, and most programs requiremore. Other work demonstrated how use Integer Linear Programming (ILP) to \emph{cluster} the operators in a general data-flow graph into subgraphs that can be individually fused, but until now this approach did not handle operations like filter, which produce arrays of a different size than their input. The technique we introduce in this paper combines the advantages of both, by  extending the existing ILP approach with support for size changing operators, using an external ILP solver to find good clusterings.

%The original abstract:
%Recent work on array fusion shows how to extract data-flow graphs from functional programs and compile them into efficient imperative loops. However, the compilation process only handles graphs that can be compiled into \emph{single} loops, and most programs require more. Prior work shows how use Integer Linear Programming (ILP) to \emph{cluster} the operators in a general data-flow graph into subgraphs that can be individually fused, but until now this approach did not handle operations like filter, which produce arrays of a different size than their input. We extend the existing ILP approach with support for size changing operators, using an external ILP solver to find good clusterings.
\end{abstract}
